---
title: "Appendix"
author: ""
date: ""
output: html_document
---

```{r setup, include=FALSE, echo = FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, echo = FALSE, message=FALSE}
#Load Packages
library(ggplot2)
library(tidyverse)
```

```{r, echo=FALSE, message=FALSE, include = FALSE}
#Create a data frame
gas_df <- read_csv("Gas_Data.csv")
gas_df
```
###I. Supply, Demand, and Marginal Externality Costs for Gasoline in France
```{r, echo=FALSE, include=FALSE, message=FALSE, warning = FALSE}


#Create demand curve for High and Low
#demand_high <- ggplot(gas_df, aes(x = Q_Low_Gallons_per_Day, y = Price_Dollars)) + 
 # geom_line(color = "#0073D9", size = 1) + 
 # theme_classic() 
#demand_high



#Create a linear regression
demand_high_lm <- lm(Price_Dollars ~ gas_df$Q_High_Gallons_per_Day, data = gas_df)
demand_high_lm

demand_low_lm <- lm(Price_Dollars ~ gas_df$Q_Low_Gallons_per_Day, data = gas_df)
demand_low_lm



#Set Coefficients

#High Demand Coefficients
demand_high_lm$coefficients
bh = demand_high_lm$coefficients[1]
bh
mh = (demand_high_lm$coefficients[2])
mh

#High Demand Equation
#ph = bh - mh(q)
#ph = 23.3914418-0.0001297(q)

qhighA <- (1/mh) # 1/slope or m for high income
qhighB <- (bh/-mh) # intercept or b/ - slope or m for high income

#Low Demand Coefficients
demand_low_lm$coefficients
bl = demand_low_lm$coefficients[1]
ml = (demand_low_lm$coefficients[2])
ml

#Low Demand Equation
#pl = bl - ml(q)
#pl = 21.9908534-0.0001355(q)

qlowA <- (1/ml) # 1/slope or m for low income
qlowB <- (bl/-ml) # intercept or b/ - slope or m for low income



#Make Demand Curves
demand_eq_high <- function(q) {23.3914418-0.0001297*q}
demand_eq_low <- function(q) {21.9908534-0.0001355*q}



#Find aggregate demands separately for quantity
Q_aggb<- qlowB + qhighB # aggregate for intercept
Q_aggm<- qlowA + qhighA # aggregate for slope



#Find aggregate demand separately for price
P_aggb<- -Q_aggb/Q_aggm # aggregate for intercept
P_aggb
P_aggm<- 1/Q_aggm # aggregate for slope
P_aggm
p_aggregate <- function(p) {(P_aggb+P_aggm*p)}


# Find aggregate demand curve
q_aggregate <- function(q){P_aggb+P_aggm*q}



#Find MPC (supply curve) with price, $5.00
supply<- 5/((5-P_aggb)/P_aggm)
supply




# Find marginal external cost
mec <- function(y) {2}



# List out functions
demand_eq_highgph <- function(q) {23.3914418-0.0001296638*q}
demand_eq_lowgph <- function(q) {21.9908534-0.0001355174*q}
mpcgph <- function(q) {supply*q}
mecgph <- function(y) {2}
q_aggregategph <- function(q){P_aggb+P_aggm*q}


```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
# Graph curves
opt<- data.frame(x = c(0:267217.1), y = c(5))
x<- 70000:500000
demand_gph <- ggplot(data.frame(x = c(70000:400000)), aes(x=x, colour=Function)) +
  scale_colour_identity("Function", guide="legend")+
   stat_function(fun=mpcgph, geom = "line", aes(colour ="MPC")) +
  stat_function(fun=demand_eq_highgph, geom="line", aes(colour ="High Demand")) +
  stat_function(fun=demand_eq_lowgph, geom="line", aes(colour ="Low Demand")) +
  stat_function(fun=q_aggregategph, geom = "line", aes(colour ="Agg. Demand")) +
  stat_function(fun=mecgph, geom = "line", aes(colour ="MEC")) +
  xlab("\nQuantity (Gallons per Day)")+
  ylab("Price ($USD)\n")+
  ggtitle("Gas Market Under the Status Quo \n")+
  scale_y_continuous(limits = c(0,25), expand = c(0,0))+
  scale_x_continuous(limits = c(0,400000), expand = c(0,0), breaks = seq(0, 400000, 50000)) +
  theme_classic() + scale_colour_manual("Functions", values = c("darkolivegreen3", "darkorange3","goldenrod1","red3","chartreuse4"))

demand_gph
```

#####Figure 1. The gas market for France was analyzed by determining the high and low income demand curves, the aggregate demand curve, the marginal private cost for gasoline producers, and the marginal external costs derived from impacts to human health and the environment.

####Equations for Figure 1.
High Income Demand: $P = (23.3914418-0.0001296638(Q))$ 

Low Income Demand: $P = (21.9908534-0.0001355174(Q))$

Aggregate Demand: $P = (22.70661-0.00006626299(Q))$

Marginal Private Cost: $P = (0.00001871138(Q))$

Marginal External Cost: $P = 2.00$


###II. Costs and Benefits at Status Quo

####Equations for Benefits

Surplus General Calculation: $S = (1/2)(P)(Q)$

Aggregate Consumer Surplus: $CS = (1/2)(22.70661 - 5.00)(267217.062558)$ = $2,365,754

High Income Consumer Surplus: $CS = (1/2)(23.3914418 - 5.00)(141799.9)$ = $1,303,952

Low Income Consumer Surplus: $CS = (1/2)(21.9908534 - 5.00)(125393.8)$ = $1,065,274

Producer Surplus: $PS = (1/2)(5.00)(267217.062558)$ = $668,043

####Equations for Costs

TEC General Calculation: $TEC = (MEC)(Q)$

Total Environmental Cost: $TEC = (2.00)(267217.062558)$ = $534,434

```{r, include = FALSE, echo = FALSE, message = FALSE}
#Determine the aggregate consumer benefit

#Determine the market equilibrium point, when aggregate demand = supply
#At equilibrium: p = $5.00, q = 267217.062558
### 

#Aggregate equation =
#Q = 267217.062558
#Y intercept of agg demand
q_aggregategph(0)
# = 22.70661


#Double check the area using shapes
agg_height_cs <- 22.70661 - 5
agg_base_cs <- 267217.062558
aggregate_cs_geom <- (1/2)*agg_base_cs*agg_height_cs 
aggregate_cs_geom
# = $2365754

```



```{r, include = FALSE}
#Calculate the produce benefits
agg_height_ps <- 5
agg_base_ps <- 267217.062558
aggregate_ps_geom <- (1/2)*agg_height_ps*agg_base_ps
aggregate_ps_geom
# = $668042.7
```


```{r, include = FALSE}
#Calculate the environmental cost
ec_height <- 2
ec_base <- 267217.062558
ec_geom <- ec_height*ec_base
ec_geom
# = $534434.1
```


```{r, include = FALSE}
#Distribution of Benefits
# Find q for high income at $5.00
#ph <- 23.3914418-0.0001297*(q)
# 5 = 23.3914418-0.0001297*(q)
q_at_equil_h <- (5-23.3914418)/(-0.0001297)
q_at_equil_h
#q = 141799.9
demand_eq_high(141799.9)
#4.999995 ~ $5.00 check

#Calculate the high demand at equilibrium
height_equil_h <- 23.3914418 - 5
base_equil_h <-141799.9
cs_equil_h <- (1/2)*height_equil_h*base_equil_h 
cs_equil_h
# = $1303952


#Find q for low income at $5.00
#pl <- 21.9908534-0.0001355*q
#5 = 21.9908534-0.0001355*q
q_at_equil_l <- (5-21.9908534)/(-0.0001355)
q_at_equil_l

height_equil_l <- 21.9908534 - 5
base_equil_l <- 125393.8
cs_equil_l <- (1/2)*height_equil_l*base_equil_l 
cs_equil_l
# =  $1065274


# Find the difference in benefits
benefits_difference = 1303952-1065274
benefits_difference
# = $238678
```

###III. Costs and Benefits with a $0.50/gallon Tax

####Equations for Benefits

Surplus General Calculation: $S = (1/2)(P)(Q)$

High Income Consumer Surplus: $CS = (1/2)(23.3914418 - 5.3899)(138793.7)$ = $1,249,250

Low Income Consumer Surplus: $CS = (1/2)(21.9908534 - 5.3899)(122516.3)$ = $1,016,944

Producer Surplus: $PS = (1/2)(5.3899-.50)(261333)$ = $638,946

Tax Revenue General Calculation: $R = (Price~with~Tax - Price)(Q)$

Tax Revenue = $R = (5.3899-4.8899)(261333)$ = $130,667

####Equations for Costs

Marginal Private Cost: $P = 0.50 + 00001871138(Q)$

TEC General Calculation: $TEC = (MEC)(Q)$

Total Environmental Cost: $TEC = (2.00)(261333)$ = $522,666





```{r, include = FALSE, echo = FALSE, message = FALSE}
#MPC (supply) curve changes
#Originial -> MPC = 1.871138e-05*q
#New -> MPC = 1.871138e-05*q+ 0.50

mpc_tax <- function(q) {1.871138e-05*q+ 0.50}

#Find the new market equilibrium point
# Set new supply to demand

q_agg_tax <- (P_aggb-0.50)/(supply+-P_aggm)
q_agg_tax
# = 261333 gallons (261333.0349 w/ calculator)

#Find the new price at the equilibrium point
#q_aggregategph <- function(q){P_aggb+P_aggm*q}
p_agg_tax <- q_aggregategph(q_agg_tax)
p_agg_tax 
# = $5.3899


#Find the consumer surplus for high income
q_at_tax_h <- (5.3899-23.3914418)/(-0.0001297)
q_at_tax_h
#q = 138793.7
demand_eq_high(q_at_tax_h)

#Calculate the high demand CS at new price
height_tax_h <- 23.3914418 - 5.3899
base_tax_h <- 138793.7
cs_tax_h <- (1/2)*height_tax_h*base_tax_h 
cs_tax_h
# = $1249250

#Find the consumer surplus for low income
q_at_tax_l <- (5.3899-21.9908534)/(-0.0001355)
q_at_tax_l
#q = 122516.3

#Calculate the low demand CS at new price
height_tax_l <- 21.9908534 - 5.3899
base_tax_l <- 122516.3
cs_tax_l <- (1/2)*height_tax_l*base_tax_l
cs_tax_l
# = $1016944

#Calculate the producer surplus at new price
agg_height_ps_tax <- 5.3899-.50
agg_base_ps_tax <- 261333
aggregate_ps_geom_tax <- (1/2)*agg_height_ps_tax*agg_base_ps_tax
aggregate_ps_geom_tax
# = $638946.1

#Calculate the environmental cost with the new tax
tec_tax <- (2*261333)
tec_tax
# = $522666

#Calculate the total revenue with the tax
#Calculate the price with new quantity at tax
rev_price <- mpcgph(q_agg_tax)
rev_price
#4.8899

#Calculate the revenue
rev_tax <- q_agg_tax*(p_agg_tax-rev_price)
rev_tax
# = $130666.5 

```




```{r, include= FALSE, messages = FALSE, echo = FALSE, warning = FALSE}
#Tax Revenue to repair infrastructure

#Create a vector for possible taxes
taxes <- seq(0.50, 5, by = 0.50)
taxes

#Create a new supply curve with possible taxes
mpc_mtaxes <- function(q) {supply + taxes}
mpc_mtaxes()

price_sq <- 5 

#Create a function to determine the quantity at equilibrium for multiple taxes 

q_mtaxes <- (P_aggb-taxes)/(supply+-P_aggm)
q_mtaxes

#Find consumerprices at multiple taxes with a function

p_mtaxes <- q_aggregategph(q_mtaxes)
p_mtaxes

#Find producer costs at multiple taxes with a function
p_mpc_mtaxes <- mpc_tax(q_mtaxes)
p_mpc_mtaxes

#Find environmental costs at multiple taxes
tec_mtaxes <- (2*q_mtaxes)

#Find producer revenues at multiple taxes

rev_price_mtaxes <- mpcgph(q_agg_tax)
rev_price_mtaxes

rev_mtaxes <- (p_mtaxes-price_sq)*q_mtaxes
rev_mtaxes 

#Find revenue for consumers
rev_con <- (p_mtaxes-price_sq) * q_mtaxes
```
###IV. Costs and Benefits with Multiple Taxes

####Equations for Benefits

a = Sum of All 

Tax Revenue General Calculation: $R = (Price~with~Tax_a- Price_a)(Q)$ = $130,667

####Equations for Costs

Total Environmental Cost: $TEC = (2.00)(Qa)$ = $522,666

```{r, echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}

#Find the consumer surplus for high income these taxes

q_highd <- function(p) {(bh/-mh)-(p/-mh)}
q_high_mtaxes <- q_highd(p_mtaxes)
q_high_mtaxes

area_h_mtaxes <- function(q) {integrate(demand_eq_highgph, lower = 0, upper = q)$value}
high_areas_mtaxes <- sapply(q_high_mtaxes, area_h_mtaxes)

# Cost
cost_high_mtaxes <- q_high_mtaxes * p_mtaxes

# Calculate CS:
cs_high_mtaxes <- (high_areas_mtaxes - cost_high_mtaxes) + rev_con
cs_high_mtaxes



#Find the consumer surplus for low income these taxes

q_lowd <- function(p) {(bl/-ml)-(p/-ml)}
q_low_mtaxes <- q_lowd(p_mtaxes)
q_low_mtaxes

area_l_mtaxes <- function(q) {integrate(demand_eq_lowgph, lower = 0, upper = q)$value}
low_areas_mtaxes <- sapply(q_low_mtaxes, area_l_mtaxes)

# Cost
cost_low_mtaxes <- q_low_mtaxes * p_mtaxes

# Calculate CS:
cs_low_mtaxes <- (low_areas_mtaxes - cost_low_mtaxes) + rev_con - tec_mtaxes
cs_low_mtaxes


#Find the Producer Surplus


area_p_mtaxes <- function(q){integrate(mpcgph, lower = 0, upper = q)$value}
prod_areas <- sapply(q_mtaxes, area_p_mtaxes)

# Cost using the original supply curve and price at MPC
cost_mtaxes <- q_mtaxes * p_mpc_mtaxes 
cost_mtaxes
#Calculate PS:
ps_mtaxes<- (cost_mtaxes - prod_areas) + rev_mtaxes
ps_mtaxes

library(kableExtra)
#Create a data frame of the values
tax_scenarios <- as.data.frame(cbind(taxes, cs_high_mtaxes, cs_low_mtaxes, ps_mtaxes))
tax_scenarios
```

```{r, echo=FALSE}
# Create a table 
taxes_table <- kable(tax_scenarios,
                     col.names = c("Potential Tax", "High Income Consumer Surplus", "Low Income Consumer Surplus", "Producer Surplus"), align = "c") %>%
  kable_styling(bootstrap_options = c("striped", "condensed", "centered"))
taxes_table
```
###V. Costs and Benefits with the Introduction of Electric Vehicles

High Income Demand: $P = (11.69572-0.0001296638(Q))$ 

Low Income Demand: $P = (10.99543-0.0001355174(Q))$

Price: $P = (11.3533-00006626299(Q))$ = $4.87

####Equations for Benefits

Surplus General Calculation: $S = (1/2)(P)(Q)$

High Income Consumer Surplus: $CS = (1/2)(11.69572 - 4.87)(51639.09)$ = $176,237

Low Income Consumer Surplus: $CS = (1/2)(10.99543 - 4.87)(46238.27)$ = $141,615

####Equations for Costs

TEC General Calculation: $TEC = (MEC)(Q)$

Total Environmental Cost: $TEC = (2.00)(97877.36)$ = $195,755

```{r, include = FALSE}
#Cut original demand curve in half for electric vehicles

#Cut the demand intercepts in half for high and low income
demand_eq_highgph <- function(q) {23.3914418-0.0001296638*q}
demand_eq_lowgph <- function(q) {21.9908534-0.0001355174*q}

#Cut the high income
new_int_h <- (23.3914418/2)
new_int_h
demand_high_half <- function(q) {11.69572-0.0001296638*q}

#Cut the low income
new_int_l <- (21.9908534/2)
new_int_l
demand_low_half <- function(q) {10.99543-0.0001355174*q}


#Find new surpluses at $5.00 but half the demand for high
q_at_half_h <- (4.87-11.69572)/(-0.0001296638)
q_at_half_h
demand_high_half(51639.09)


#Calculate the high demand at equilibrium
height_half_h <- 11.69572 - 4.87
base_half_h <- 51639.09
cs_half_h <- (1/2)*height_half_h*base_half_h 
cs_half_h
# 172880.4


#Find new surpluses at $5.00 but half the demand for low
q_at_half_l <- (4.87-10.99543)/(-0.0001296638)
q_at_half_l
demand_low_half(46238.27)


#Calculate the high demand at equilibrium
height_half_l <- 10.99543 - 4.87
base_half_l <- 46238.27
cs_half_l <- (1/2)*height_half_l*base_half_l
cs_half_l
# 141614.6

#Find quanity of aggregate 
q_agg_half <- base_half_h + base_half_l
q_agg_half

#Find total environmental cost
tec_half <- (2*q_agg_half)
tec_half
#195754.7


qlowA_half <- (1/ml) # 1/slope or m for low income
qlowB_half <- ((bl/2)/-ml) # intercept or b/ - slope or m for low income

qhighA_half <- (1/mh) # 1/slope or m for low income
qhighB_half <- ((bh/2)/-mh) # intercept or b/ - slope or m for low income



#Find aggregate demands separately for quantity
Q_aggb_half<- qlowB_half + qhighB_half # aggregate for intercept
Q_aggm_half<- qlowA_half + qhighA_half # aggregate for slope



#Find aggregate demand separately for price
P_aggb_half<- -Q_aggb_half/Q_aggm_half # aggregate for intercept
P_aggb_half
P_aggm_half<- 1/Q_aggm_half # aggregate for slope
P_aggm_half
p_aggregate_half <- function(p) {(P_aggb_half+P_aggm_half*p)}


# Find aggregate demand curve
q_aggregate_half <- function(q){P_aggb_half+P_aggm_half*q}
q_aggregate_half(97877.36)

```
###VI. Costs and Benefits of Gasoline with a $2.00 Tax

####Equations for Costs

TEC General Calculation: $TEC = (MEC)(Q)$

Total Environmental Cost: $TEC = (2.00)(243680.6)$ = $487,361


```{r, include=FALSE}
#MPC (supply) curve changes
#Originial -> MPC = 1.871138e-05*q
#New -> MPC = 1.871138e-05*q+ 2.00

mpc_tax_2 <- function(q) {1.871138e-05*q+ 2.00}

#Find the new market equilibrium point
# Set new supply to demand

q_agg_tax2 <- (P_aggb-2.00)/(supply+-P_aggm)
q_agg_tax2
# 243680.6 


#Find the new price at the equilibrium point
#q_aggregategph <- function(q){P_aggb+P_aggm*q}
p_agg_tax2 <- q_aggregategph(q_agg_tax2)
p_agg_tax2
# $ 6.5596


#Find the consumer surplus for high income
q_at_tax_h2 <- (6.5596-23.3914418)/(-0.0001297)
q_at_tax_h2
# 129775.2

demand_eq_high(q_at_tax_h2)

#Calculate the high demand CS at new price
height_tax_h2 <- 23.3914418 - 6.5596
base_tax_h2 <- 129775.2
cs_tax_h2 <- (1/2)*height_tax_h2*base_tax_h2 
cs_tax_h2
# $1092178

#Find the consumer surplus for low income
q_at_tax_l2 <- (6.5596-21.9908534)/(-0.0001355)
q_at_tax_l2
# 113883.8

#Calculate the low demand CS at new price
height_tax_l2 <- 21.9908534 - 6.5596
base_tax_l2 <- 113883.8
cs_tax_l2 <- (1/2)*height_tax_l2*base_tax_l2
cs_tax_l2
# = $878684.9

#Calculate the producer surplus at new price
agg_height_ps_tax2 <- 6.5596-2.00
agg_base_ps_tax2 <-  243680.6 
aggregate_ps_geom_tax2 <- (1/2)*agg_height_ps_tax2*agg_base_ps_tax2
aggregate_ps_geom_tax2
# = $555543

#Calculate the environmental cost with the new tax
tec_tax2 <- (2*243680.6)
tec_tax2
# = $487361.2



```
